Optimal (Multiway) Spatial Joins

### 2024-05-24 msj.tex
yufei

We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \cross(\bm{t}, H) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \nn \\
    \cross(\bm{t}, V) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \nn
}
These sets have important properties, as proved in Appendix~\ref{app:hv}:

\begin{lemma} \label{lmm:hv:type1:properties}
    Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$. All the following statements are true:
    \myenums{
        \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.
        \item For any $h \in \cross(\bm{t}, H)$ and any $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.
        \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
    }
\end{lemma}

@@

\mytab{
    \> {\bf Algorithm Generate-$\J^*$} \\
    \> 1.\> $S = \emptyset$ \\ 
    \> 2.\> {\bf for} each $(r_1, ..., r_{k-2}) \in \Pi_{1:k-2}(\J_1(R_1,$ $...,$ $R_{k-2}, H, V))$ {\bf do} \\
    \> 3.\>\> define $B, r_a$, and $r_b$ as above \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(r_a, B; H) \times \cross(r_b, B; V)$ {\bf do} \\
    \> 5.\>\>\> add $(r_1, ..., r_{k-2}, h, v)$ to $S$
}

>>>>

We now introduce:
% \myitems{
%     \item $\cross(r_a, B; H)$, the set of segments in $H$ that cross $r_a$ and $B$;
%     \item $\cross(r_b, B; V)$, the set of segments in $V$ that cross $r_b$ and $B$.
% }
\myeqn{
    \cross(\bm{t}, H) = \set{h \in H \mid \text{$h$ crosses both $B_\bm{t}$ and $\gleft(\bm{t})$}} \nn \\
    \cross(\bm{t}, V) = \set{h \in H \mid \text{$v$ crosses both $B_\bm{t}$ and $\gbot(\bm{t})$}}. \nn
}
These sets have important properties, as proved in Appendix~\ref{app:hv} (recall the notation $\bm{t}[i] = r_i'$ for each $i \in [k-2]$):

\begin{lemma} \label{lmm:hv:type1:properties}
    %Let $r_i$ be the full rectangle of $r_i'$ for each $i \in [k-2]$.
    All the following statements are true:
    \myenums{
        \item For each $\bm{t} \in \J(R_1', R'_2, ..., R'_{k-2})$, we have:

        \vspace{2mm}

        \myenums{
            \item $\cross(\bm{t}, H) \ne \emptyset$ and $\cross(\bm{t}, V) \ne \emptyset$.

            \item Let $r_i$ ($i \in [k-2]$) be the full rectangle of $\bm{t}[i']$. Then,
            for any $h \in \cross(\bm{t}, H)$ and any $v \in \cross(\bm{t}, V)$, the $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J(R_1, ..., R_{k-2}, H, V)$.

            \item If a $k$-tuple $(r_1, r_2, ..., r_{k-2}, h, v)$ belongs to $\J_1$, then $h \in \cross(\bm{t}, H)$ and $v \in \cross(\bm{t}, V)$.
        }

        \vspace{2mm}

        \item $\sum_{\bm{t}} |\cross(\bm{t}, H)| \le \out$ and $\sum_{\bm{t}} |\cross(\bm{t}, V)| \le \out$.
    }
\end{lemma}

@@

\mytab{
    \> {\bf Algorithm Generate-$\J^*$} \\
    \> 1.\> $\J^* = \emptyset$ \\
    \> 2.\> {\bf for} each $(k-2)$-tuple $\bm{t} \in \J(R_1,$ $...,$ $R_{k-2}))$ {\bf do} \\
    \> 3.\>\> $r_i \leftarrow$ the full rectangle of $\bm{t}[i]$, for each $i \in [k-2]$ \\
    \>\>\> /* recall that $\bm{t}[i]$ is the $i$-th rectangle in $\bm{t}$ */ \\
    \> 4.\>\> {\bf for} each $(h, v) \in \cross(\bm{t}, H) \times \cross(\bm{t}, V)$ {\bf do} \\
    \> 5.\>\>\> add $(r_1, ..., r_{k-2}, h, v)$ to $\J^*$
}
